Formal Modelling of Predator Preferences using Molecular Gut-Content Analysis

### 2015-05-11 paper/main.tex
more changes in Discussion

Throughout this paper we assume the observed data were generated from underlying Poisson distributions.  Though this assumption is not easily tested, and other factors affecting our model may distort our methods, e.g.\ sampling issues, environmental variables, differential decay rates, we do not believe a better assumption is readily available to handle all the cases we considered.  The Poisson distribution provides reasonable biological interpretation to the available data, data obtained by ecologists interested in prey electivity.  One could hypothesize a more complex distribution that similarly has good biological interpretation, say a distribution with more than one parameter.  This may perform better than our model when full count data are observed.  But when only unobserved count data is available, any distribution with more than one parameter is unidentifiable.  Further, because the Poisson distribution {\color{red} SAY SOMETHIGN}, the EM algorithm is theoretically guaranteed to converge to the parameters of interest {\color{red} CITATION? Hoeting and Givens}.  Future development of our methods might consider more complex distributions to handle variables not presently considered in the case of fully observed count data.

>>>>

Throughout this paper we assume the complete data were generated from underlying Poisson distributions.  Though this assumption is not easily tested, and other factors affecting our model may distort our methods, e.g.\ sampling issues, environmental variables, differential decay rates, we do not believe a better assumption is readily available to handle all the cases we considered.  The Poisson distribution provides reasonable biological interpretation to the available data, data obtained by ecologists interested in prey electivity.  One could hypothesize a more complex distribution that similarly has good biological interpretation, say a distribution with more than one parameter.  Such a distribution could theoretically perform better than our model when full count data are observed and the sampled data were not generated from a Poisson distribution -- if the data were generated from a Poisson distribution then our likelihood ratio test ensures we are using the most powerful test available.  But when only unobserved count data is available, any distribution with more than one parameter is unidentifiable.  The Poisson distribution on the other hand allowed us to use a relatively simple EM algorithm to estimate parameters of interest when only unobserved count data are available.  Future development of our methods might consider more complex distributions to handle variables not presently considered in the case of fully observed count data.
